---
title: "hw1"
output: github_document
date: "2023-09-22"
---

# Problem 1

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```
### Variables in this dataset

```{r}
skimr::skim(early_january_weather)
```
### Size of the dateset

```{r}
nrow(early_january_weather)

ncol(early_january_weather)
```
### Mean temperature
```{r}
mean(early_january_weather$temp)
```
### Scatterplot
```{r}

ggplot(early_january_weather, aes(x = time_hour, y = temp)) + geom_point(aes(col = humid)) + labs(y = "Temperature", x = "Time", title = "Different Time Temperature")

ggsave("scatter_plot.pdf")

```

### Short description

###### In the early_january_weather dataset, there are 385 observations and 15 variables. 
###### The mean temperature is 39.58 
###### The name of the variables are: origin, year month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour. 
###### There are a lot of missing data under the varibales wind_gust and pressure. 
###### From the scatterplot, the temperature is increasing over time, but the humidity varys. 

# Problem 2
```{r}
library(tidyverse)

df = tibble(
  vec_numeric = rnorm(10), 
  vec_logical = vec_numeric > 0,
  vec_char = c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten"), 
  vec_factor = factor(c( "large", "small", "medium", "medium", "large", "small", "large", "small", "small", "medium"))
)

mean_vec_numeric <- pull(df, vec_numeric)
mean(mean_vec_numeric)

mean_vec_logical <- pull(df, vec_logical)
mean(mean_vec_logical)

```
###### The mean of random sample and logical vector works, but the mean of character vector cannot be taken. The variables for vec_char and vec_factor are character values. We can only calculate the mean for numerical values.

```{r, eval=FALSE}
rv <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")
rf <- factor(rv)
x <- as.numeric(rf)
x
```


```{r, eval=FALSE}

vec_logical <- c("large", "small", "medium", "medium", "large", "small", "large", "small", "small", "medium")
vec_num <- as.numeric(vec_logical)
vec_logical

```

##### The as.numeric function converts a character vector into a numeric vector.